### 2013-04-03 doc/final_report/design.tex
Corrected some tense stuff

Given the project objectives identified in \ref{sec:objectives}, four primary
use cases were identified for Partridge as shown in Figure \ref{fig:use_cases}.
Users of Partridge are likely to be researchers who want to find and read
scientific papers. This would involve querying the database for relevant
papers, viewing metrics on the papers that have been used to classify them and
also downloading the original paper for reading.

Authors are the subset of users who may remain interested in using the query
functionality of Partridge, but also may wish to upload papers to Partridge and
add them to the corpus.

@@

From the outset, the aim was that Partridge would be a web-based tool.
Web-based systems can generally be run on any computer with access to the
internet and a modern web browser. This also means that there is no need for
the end user to install or configure extra software on their computers, making
Partridge accessible to non-technical users and those who have aggressive
software restrictions on their computers, such as GPs and the users of public
computers in libraries or on academic sites.

In order to function as a website, Partridge needed to be developed as a server
application that produced Hyper Text Markup Language (HTML) output with which a web
browser could interpret and display. The browser rendering the forms must then
communicate with a backend system capable of querying and returning papers to
the user based on their input. This lead to the decision to split the development
of Partridge into two core components: the Web Frontend comprising of user
interface elements and presentation logic and the Web Backend comprising of
intelligent systems to classify, filter and query papers using some of the NLP
techniques discussed previously.

One of the main requirements for a web server is that it responds to requests
relatively quickly, ideally within 10 seconds or less. If the response is any
slower than this, the user may get impatient and give up trying to use the
system, or in some cases, their web browser may timeout and stop trying to load
the page. Unfortunately, many of the processes involved in extracting meaningful CoreSC
information from papers are very slow. This means that processing papers
during web requests is not really feasible, since it may take several minutes
for a single paper to be annotated and classified. Therefore, a third core
component was identified: a paper preprocessor service that runs on the server
and converts, annotates and classifies papers as soon as they are uploaded.

@@

The final stage in the preprocessor pipeline is paper classification. During
this stage, features wil be extracted from the papers and used to classify the
paper in three different ways. The paper's type: case study or review paper
etc. will be determined using the presence or absence of different CoreSC labels
within the paper and their relative proportions. The subject of paper will be
determined by the presence of domain specific nouns and adjectives within the
paper. For example, a biology paper might contain words such as 'enzyme' or 'amino
acid.' The result of the paper, i.e. whether the paper was conclusive and if the
results were positive or negative, will be detected through the presence or absence
of words with a strong sentiment polarity as discussed by Wilson et al
(2005)\cite{Wilson05Polarity}. The results from the whole process are then
passed into the data store and saved.

>>>>

Given the project objectives identified in \ref{sec:objectives}, four primary
use cases were identified for Partridge as shown in Figure \ref{fig:use_cases}.
Users of Partridge were determined to be researchers who want to find and read
scientific papers. This would involve querying the database for relevant
papers, viewing metrics on the papers that have been used to classify them and
also downloading the original paper for reading.

Authors were defined as the subset of users who may remain interested in using
the query functionality of Partridge, but also may wish to upload papers to
Partridge and add them to the corpus.

@@

From the outset, the aim was that Partridge would be a web-based tool.
Web-based systems can generally be run on any computer with access to the
internet and a modern web browser. This also means that there would be no need for
the end user to install or configure extra software on their computers, making
Partridge accessible to non-technical users and those who have aggressive
software restrictions on their computers, such as GPs and the users of public
computers in libraries or on academic sites.

In order to function as a website, Partridge needed to be developed as a server
application that produced Hyper Text Markup Language (HTML) output with which a web
browser could interpret and display. The browser rendering the forms would then
communicate with a backend system capable of querying and returning papers to
the user based on their input. This led to the decision to split the development
of Partridge into two core components: the Web Frontend comprising of user
interface elements and presentation logic and the Web Backend comprising of
intelligent systems to classify, filter and query papers using some of the NLP
techniques discussed previously.

One of the main requirements for a web server is that it responds to requests
relatively quickly, ideally within 10 seconds or less. If the response is any
slower than this, the user may get impatient and give up trying to use the
system, or in some cases, their web browser may timeout and stop trying to load
the page. Unfortunately, many of the processes involved in extracting meaningful CoreSC
information from papers are very slow. This meant that processing papers
during web requests was not really feasible, since it may take several minutes
for a single paper to be annotated and classified. Therefore, a third core
component was identified: a paper preprocessor service that runs on the server
and converts, annotates and classifies papers as soon as they are uploaded.

@@

The final stage in the preprocessor pipeline is paper classification. During
this stage, features will be extracted from the papers and used to classify the
paper in three different ways. The paper's type: case study or review paper
etc. will be determined using the presence or absence of different CoreSC labels
within the paper and their relative proportions. The subject of paper will be
determined by the presence of domain specific nouns and adjectives within the
paper. For example, a biology paper might contain words such as 'enzyme' or 'amino
acid.' The result of the paper, i.e. whether the paper was conclusive and if the
results were positive or negative, will be detected through the presence or absence
of words with a strong sentiment polarity as discussed by Wilson et al
(2005)\cite{Wilson05Polarity}. The results from the whole process are then
passed into the data store and saved.

### 2013-04-03 doc/final_report/methodology.tex
Corrected some tense stuff

Under the traditional `Waterfall' Software Development model, Requirements
Gathering, Analysis, Program Design, Coding, Testing and Operations were all
defined as formal phases in the development cycle. There is little flexibility
other than moving back up the waterfall to rectify mistakes after
testing\cite{Royce:1987:MDL:41765.41801}. This model was very focused on
paperwork and bureaucracy, trying to maintain a paper trail and manage risk
through accountability \emph{(Ibed)}. This approach to software development is
very heavyweight and slow and often produced software that did not match the
users' needs as a result \cite{Boehm1988}.

As an alternative to the heavyweight Waterfall approach, Beck \emph{et al.}
came up with the principle of the Agile Manifesto, favouring a lightweight and
responsive development model over the heavyweight, slow waterfall
system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
of developers and prioriting communication between team members \emph{(Ibid.)}.
This is most prominent in the Extreme Programming (XP) method of software
development. Since Partridge is an individual project, XP was not really
applicable. However, some concepts like rapid prototyping/spike work and
iterative release cycles were used as part of the Partridge development
methodology.

@@

Throughout the project, weekly meetings were held with both project
supervisors. The notes from the preceeding week were analysed and each task
discussed in depth. New tasks were then noted down along with any observations
that should be documented. These were then uploaded to the wiki the following
day or earlier. Each party present at the meeting adds their own observations
to the notes page. This page is then reviewed at the next meeting.

>>>>

Under the traditional `Waterfall' Software Development model, Requirements
Gathering, Analysis, Program Design, Coding, Testing and Operations were all
defined as formal phases in the development cycle. There is little flexibility
other than moving back up the waterfall to rectify mistakes after
testing\cite{Royce:1987:MDL:41765.41801}. This model is very focused on
paperwork and bureaucracy, trying to maintain a paper trail and manage risk
through accountability \emph{(Ibed)}. This approach to software development is
very heavyweight and slow and often produced software that did not match the
users' needs as a result \cite{Boehm1988}.

As an alternative to the heavyweight Waterfall approach, Beck \emph{et al.}
came up with the principle of the Agile Manifesto, favouring a lightweight and
responsive development model over the heavyweight, slow waterfall
system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
of developers and prioriting communication between team members \emph{(Ibid.)}.
This is most prominent in the Extreme Programming (XP) method of software
development. Since developing Partridge was an individual project, XP was not
really applicable. However, some concepts like rapid prototyping/spike work and
iterative release cycles were used as part of the Partridge development
methodology.

@@

Throughout the project, weekly meetings were held with both project
supervisors. The notes from the preceeding week were analysed and each task
discussed in depth. New tasks were then noted down along with any observations
that should be documented. These were then uploaded to the wiki the following
day or earlier. Each party present at the meeting adds their own observations
to the notes page. This page was then reviewed at the next meeting.
